---
title: "Hotel Tree"
author: "Mindy Li"
date: "11/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##### Load Libraries
```{r}
library(rsample)  # data splitting 
library(glmnet)   # implementing regularized regression approaches
library(dplyr)    # basic data manipulation procedures
library(magrittr)
library(broom)
library(forcats)
library(plyr)
library(fastDummies)
library(MASS)
```
##### Load dataset
```{r}
Data <- read.csv("/Users/mindyli/Desktop/Fall - 1 Class/Data Science of Business/Team Project/hotel_bookings.csv")
```

# Data Cleaning 
1. Replace all NAs in `children` with 0
2. Drop Variables: `arrival_date_year`,`reservation_status_date`, `reservation_status`, `assigned_room_type`
3. Assign 0 to `agent`, and `company` if contains NULL value. Assign 1 if contains any other values.
4. In the `counntry` variables, exccept for "PRT", "GBR", "FRA", "ESP", "DEU", "ITA", "IRL", combine all other countries to "Others"
5. One-Hot Encoding for certain variables
```{r}
df<-Data

df$children[is.na(df$children)] <- 0

dropVars <- names(df) %in% c("arrival_date_year","reservation_status_date", "reservation_status", "assigned_room_type") 
df<- df[!dropVars]

# `agent' and 'company', if they are equal to NULL, assign 0, otherwise 1
df$agent <- ifelse(df$agent == "NULL", 0, 1)
df$company <- ifelse(df$company == "NULL", 0, 1)

'%notin%' <- Negate('%in%')
Country = c("PRT", "GBR", "FRA", "ESP", "DEU", "ITA", "IRL")

#combine all other countries to "Others"
for (i in 1:nrow(df)) {
  if(df[i,"country"] %notin% Country) {
    df[i,"country"] = "Others"
  }
}

#One-Hot Encoding
df <- data.frame(dummy_cols(df, select_columns = c('hotel', 'arrival_date_month', 'meal', 'country', 'market_segment', 'distribution_channel', 'is_repeated_guest', 'reserved_room_type', 'deposit_type', 'customer_type', 'required_car_parking_spaces' ), remove_selected_columns = TRUE))
```

# Data Preparation (Train/Test)

separate data into train and test dataset:
```{r}
set.seed(123)

smp_size <- floor(0.8 * nrow(df))

train_ind <- sample(seq_len(nrow(df)), size = smp_size)

train <- df[train_ind, ]
test <- df[-train_ind, ]

train_x <- model.matrix(is_canceled ~ ., train)[, -1]
train_y <- train$is_canceled 

test_x <- model.matrix(is_canceled ~ ., test)[, -1]
test_y <- test$is_canceled
```


```{r}
# treeModel <- tree(is_canceled ~ ., data=train.set)
# plot(treeModel)
# text(treeModel, cex=.75)
summary(treeModel)
```

Much finer-grained than the treeModel (42 leafs against 6), and does a better job of matching the actual prices (lower error).
```{r}
# treeModel2 <- tree(is_canceled ~ ., data=train.set, mindev=0.001)
# plot(treeModel2)
# text(treeModel2, cex=.5)
# summary(treeModel2)
```
The third model selects several variables:
```{r}
# treeModel3 <- tree(is_canceled ~ required_car_parking_spaces + total_of_special_requests + previous_cancellations + agent + booking_changes + adr + arrival_date_week_number+stays_in_week_nights+ adults+previous_bookings_not_canceled , data=df, mindev=0.001)
# plot(treeModel3)
# text(treeModel3, cex=.5)
# summary(treeModel3)
```



Prediction
```{r}
# my.prediction <- predict(treeModel2, test.set) # gives the probability for each class
# head(my.prediction)
```

```{r}
# # Point prediction
# # Let's translate the probability output to categorical output
# maxidx <- function(arr) {
#     return(which(arr == max(arr)))
# }
# idx <- apply(my.prediction, c(1), maxidx)
# prediction <- c('is_canceled')[idx]
# table(prediction, test.set$is_canceled)
```

```{r}
# cv.model <- cv.tree(treeModel2)
# plot(cv.model)
```

```{r}
# cv.model$dev  # gives the deviance for each K (small is better)
# ```
# ```{r}
# best.size <- cv.model$size[which(cv.model$dev==min(cv.model$dev))] # which size is better?
# best.size
# ```
# ```{r}
# # let's refit the tree model (the number of leafs will be no more than best.size)
# cv.model.pruned <- prune.misclass(treeModel2, best=best.size)
# summary(cv.model.pruned)
```

```{r}
# Classification Tree with rpart
library(rpart)

# grow tree
fit <- rpart(is_canceled ~. , method="class", data=train)

printcp(fit) # display the results
plotcp(fit) # visualize cross-validation results
summary(fit) # detailed summary of splits

# plot tree
plot(fit, uniform=TRUE,
   main="Classification Tree for Hotel Cancellation")
text(fit, use.n=TRUE, all=TRUE, cex=.8)

```

```{r}
fit.predict <- predict(fit, newx=test)
summary(fit.predict)
fit.predict
#roc(test_y,fit.predict)
```

















