---
title: "Hotel-Booking Logistic Regression"
author: "Mindy Li"
date: "11/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##### Load Libraries
```{r}
library(rsample)  # data splitting 
library(glmnet)   # implementing regularized regression approaches
library(dplyr)    # basic data manipulation procedures
library(magrittr)
library(broom)
library(forcats)
library(plyr)
library(fastDummies)
library(MASS)
```
##### Load dataset
```{r}
Data <- read.csv("/Users/mindyli/Desktop/Fall - 1 Class/Data Science of Business/Team Project/hotel_bookings.csv")
```

# Data Cleaning 
1. Replace all NAs in `children` with 0
2. Drop Variables: `arrival_date_year`,`reservation_status_date`, `reservation_status`, `assigned_room_type`
3. Assign 0 to `agent`, and `company` if contains NULL value. Assign 1 if contains any other values.
4. In the `counntry` variables, exccept for "PRT", "GBR", "FRA", "ESP", "DEU", "ITA", "IRL", combine all other countries to "Others"
5. One-Hot Encoding for certain variables
```{r}
df<-Data

df$children[is.na(df$children)] <- 0

dropVars <- names(df) %in% c("arrival_date_year","reservation_status_date", "reservation_status", "assigned_room_type") 
df<- df[!dropVars]

# `agent' and 'company', if they are equal to NULL, assign 0, otherwise 1
df$agent <- ifelse(df$agent == "NULL", 0, 1)
df$company <- ifelse(df$company == "NULL", 0, 1)

'%notin%' <- Negate('%in%')
Country = c("PRT", "GBR", "FRA", "ESP", "DEU", "ITA", "IRL")

#combine all other countries to "Others"
for (i in 1:nrow(df)) {
  if(df[i,"country"] %notin% Country) {
    df[i,"country"] = "Others"
  }
}

#One-Hot Encoding
#df <- data.frame(dummy_cols(df, select_columns = c('hotel', 'arrival_date_month', 'meal', 'country', 'market_segment', 'distribution_channel', 'is_repeated_guest', 'reserved_room_type', 'deposit_type', 'customer_type', 'required_car_parking_spaces' ), remove_selected_columns = TRUE))
```

# Data Preparation (Train/Test)

separate data into train and test dataset:
```{r}
set.seed(123)

smp_size <- floor(0.8 * nrow(df))

train_ind <- sample(seq_len(nrow(df)), size = smp_size)

train <- df[train_ind, ]
test <- df[-train_ind, ]

train_x <- model.matrix(is_canceled ~ ., train)[, -1]
train_y <- train$is_canceled 

test_x <- model.matrix(is_canceled ~ ., test)[, -1]
test_y <- test$is_canceled
```

```{r}
lr <- lm(is_canceled ~ ., data = train)
```

```{r}
summary(lr)
```

```{r}
lrPred <- prediction(predict(lr, newx= test))
```


```{r}
roc(test, lrPred, plot = TRUE, legacy.axes = TRUE,percent = TRUE, xlab = "False Positive Percentage", ylab="True Positive Percentage",col="#377eb8", lwd=4,print.auc=TRUE,main =  "Logistic")
```

```{r}
lr$
```



