---
title: "Hotel Booking-Random Forest"
author: "Mindy Li"
date: "11/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##### Load Libraries
```{r}
library(rsample)  # data splitting 
library(ggplot2)   # implementing regularized regression approaches
library(dplyr)    # basic data manipulation procedures
library(magrittr)
library(broom)
library(forcats)
library(plyr)
library(fastDummies)
library(MASS)
library(cowplot)
library(randomForest)
```
##### Load dataset
```{r}
Data <- read.csv("/Users/mindyli/Desktop/Fall - 1 Class/Data Science of Business/Team Project/hotel_bookings.csv")
```

# Data Cleaning 
1. Replace all NAs in `children` with 0
2. Drop Variables: `arrival_date_year`,`reservation_status_date`, `reservation_status`, `assigned_room_type`
3. Assign 0 to `agent`, and `company` if contains NULL value. Assign 1 if contains any other values.
4. In the `counntry` variables, exccept for "PRT", "GBR", "FRA", "ESP", "DEU", "ITA", "IRL", combine all other countries to "Others"
5. One-Hot Encoding for certain variables
```{r}
df<-Data

df$children[is.na(df$children)] <- 0

dropVars <- names(df) %in% c("arrival_date_year","reservation_status_date", "reservation_status", "assigned_room_type") 
df<- df[!dropVars]

# `agent' and 'company', if they are equal to NULL, assign 0, otherwise 1
df$agent <- ifelse(df$agent == "NULL", 0, 1)
df$company <- ifelse(df$company == "NULL", 0, 1)

'%notin%' <- Negate('%in%')
Country = c("PRT", "GBR", "FRA", "ESP", "DEU", "ITA", "IRL")

#combine all other countries to "Others"
for (i in 1:nrow(df)) {
  if(df[i,"country"] %notin% Country) {
    df[i,"country"] = "Others"
  }
}

```



```{r}
#One-Hot Encoding
df <- data.frame(dummy_cols(df, select_columns = c('hotel', 'arrival_date_month', 'meal', 'country', 'market_segment', 'distribution_channel', 'is_repeated_guest', 'reserved_room_type', 'deposit_type', 'customer_type', 'required_car_parking_spaces' ), remove_selected_columns = TRUE))
#df$is_canceled <- as.factor(ifelse(test=df$is_canceled == 0, yes= "Not Canceled", no="Canceled"))
df$is_canceled <- as.factor(df$is_canceled)
```

```{r}
#str(df)
```

```{r}
# # 'hotel', 'arrival_date_month', 'meal', 'country', 'market_segment', 'distribution_channel', 'is_repeated_guest', 'reserved_room_type', 'deposit_type', 'customer_type', 'required_car_parking_spaces' 
# for(i in 1:ncol(df)) {
#   if(df[,])
# }
# df$hotel_City.Hotel <- as.factor
```


# Data Preparation (Train/Test)

separate data into train and test dataset:
```{r}
set.seed(123)

smp_size <- floor(0.8 * nrow(df))

train_ind <- sample(seq_len(nrow(df)), size = smp_size)

train <- df[train_ind, ]
test <- df[-train_ind, ]

train_x <- model.matrix(is_canceled ~ ., train)[, -1]
train_y <- train$is_canceled 

test_x <- model.matrix(is_canceled ~ ., test)[, -1]
test_y <- test$is_canceled
```

# RandomForest
```{r}
rfModel <- randomForest(is_canceled~., data=train)
```

```{r}
rfModel
```

```{r}
rfModel.predicted <- predict(rfModel, newx=test, type = "prob")
#roc(test_y, rfModel.predicted, plot = TRUE, legacy.axes = TRUE,percent = TRUE, xlab = "False Positive Percentage", ylab="True Positive Percentage",col="#377eb8", lwd=4,print.auc=TRUE,main =  "Random Forest")
```

```{r}
# table(rfModel.predicted)
# table(test$is_canceled)
head(rfModel$err.rate)
tail(rfModel$err.rate)
str(rfModel$predicted)
```


```{r}
oob.error.data <- data.frame(
  Trees=rep(1:nrow(rfModel$err.rate), times=3),
  Type=rep(c("OOB", "Not Canceled", "Canceled"), each=nrow(rfModel$err.rate)),
  Error=c(rfModel$err.rate[,"OOB"], 
    rfModel$err.rate[,"0"], 
    rfModel$err.rate[,"1"]))
oob.error.data

ggplot(data=oob.error.data, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))
```

```{r}
library(pROC)
#par(pty = "s")
test$is_canceled <- as.factor(as.character(test$is_canceled))
roc(test_y, rfModel$predicted)
```


```{r}
#rfModel$votes
importance(rfModel)

```
```{r}
table(test_y)
```

























